Precise Weed and Maize Classification through Convolutional Neuronal Networks

### 2017-08-19 PaperBCJ.tex

In order to have adequate image processing that could be implemented to work in real time, the number of the network filter layers was reduced from 64 to 16, achieving to reduce the number of parameters to be computed during the classification. A classification time reduced by 2.5 times compared the original Net of 64 filters was obtained. This change had a small impact in the training accuracy of the net, its value increased 1 \% in comparison to the original net. \\

@@

This paper presented an analysis of a Convolutional Neuronal Networks application for classification between maize plants and weeds. With this purpose, several CNN Architectures were tested, the network that presented the best results was cNET of 16 filters, with a 97.23 \% of training accuracy, using a dataset of both classes of 44580 segmented images. \\

@@

Also, by using different methods to classify the images in our experiments the results showed that the best time of classification was achieved by using a Nvidia Graphics Card. This was due to the parallel architecture that this GPU has. Also, this Graphics Card is fully supported for the computational platform CUDA, it demonstrated to be 18 times faster than a normal CPU and 170 times faster than a Raspberry Pi 3. \\

@@

The study demonstrated that is better to perform some geometrical transformations to the dataset images due to the benefits it offers, such as the improvement in plant classification since the plants will have different orientations in the crop field. \\

@@

The use of Multithreading and Batching through the library OpenBLAS is very beneficial in the case of using CPU, increasing the speed of processing in the percentage higher than 20 \%. However with the Raspberry Pi, a minimum improvement was obtained, instead the use of GPU was prejudicial because it causes the speed to be reduced considerably. \\

@@

In the case of implementing the algorithm in an embedded system, it is not recommended to work with a processor like Raspberry Pi 3 for now(due they are promising advances in external Deep Lerning devices for embedded systems such as the Intel Movidius Neural Compute Stick), because it has a very slow processing because the frames per second needed to analyze the images is significantly low, so you should choose a card that has GPU, without the need for Multithreading and Batching. \\

>>>>

In order to have adequate image processing that could be implemented to work in real time, the number of network filter layers was reduced from 64 to 16, reducing the number of parameters to be computed during the classification. A classification time reduced by 2.5 times compared the original Net of 64 filters was obtained. This change had a small impact in the training accuracy of the net, its value increased 1 \% in comparison to the original net. \\

@@

This paper presented an analysis of a Convolutional Neuronal Network application for classification between maize plants and weeds. With this purpose, several CNN Architectures were tested, the network that presented the best results was cNET of 16 filters, with a 97.23 \% of training accuracy, using a dataset of both classes of 44580 segmented images. \\

@@

Also, by using different methods to classify images, the results showed that the best classification time was achieved by using a Nvidia Graphics Card. This was due to the parallel architecture that this GPU has. Also, this Graphics Card is fully supported for the computational platform CUDA, it demonstrated to be 18 times faster than a normal CPU and 170 times faster than a Raspberry Pi 3. \\

@@

The study demonstrated that performimg geometrical transformations to the dataset images improves plant classification accuracy since the plants will have different orientations in the crop field. \\

@@

The use of Multithreading and Batching through the library OpenBLAS is beneficial when using a CPU, increasing the processing speed higher than 20 \%. In contrast, a minimum improvement was obtained with the Raspberry Pi. On the contrary, the use of a GPU was prejudicial because it reduces the processing speed considerably. \\

@@

For implementing the algorithm in an embedded system, it is not recommended to work with a processor such as the Raspberry Pi 3 at the moment. This embedded system has a very slow processing speed because the frames per second used to analyze the images are significantly low, so a card that has GPU should be chosen, without the need for Multithreading and Batching. Even though there are promising advances in external Deep Lerning devices for embedded systems such as the Intel Movidius Neural Compute Stick, these systems are not yet available.  \\
